---
format:
  dashboard:
    orientation: columns
    scrolling: true
---

```{r}
#| message: FALSE
library(dplyr)
library(purrr)
library(stringr)
library(plotly)
library(Luciernaga)
library(lubridate)

CSV <- data_path <-                                                
    paste(                                                  
      "https://raw.githubusercontent.com",                  
      "UMGCCFCSS", "InstrumentQC",                   
      "main", "data", "4L", "Archive", "BeadData4L.csv",                              
      sep = "/"                                             
    ) 

TheList <- c("4L")

Data <- read.csv(CSV, check.names=FALSE)
Data$DateTime <- lubridate::ymd_hms(Data$DateTime)
#tail(Data, 1)

QC_Cutoffs <- data_path <-                                                
    paste(                                                  
      "https://raw.githubusercontent.com",                  
      "UMGCCFCSS", "InstrumentQC",                   
      "main", "data", "QC_4L.CSV",                              
      sep = "/"                                             
    )

#QC_Cutoffs <- readLines(QC_Cutoffs)
```

```{r}
MaintenancePath <- data_path <-                                                
    paste(                                                  
      "https://raw.githubusercontent.com",                  
      "UMGCCFCSS", "InstrumentQC",                   
      "main", "AuroraMaintenance.csv",                              
      sep = "/"                                             
    )
Maintenance <- read.csv(MaintenancePath, check.names=FALSE)
Maintenance <- Maintenance %>% filter(!str_detect(reason, "lean"))
Maintenance <- Maintenance %>% filter(instrument %in% TheList)
```

```{r}
The2020 <- Data |> dplyr::filter(year(DateTime) == 2020)

The2020 <- HolisticToArchived(data=The2020, manufacturer="Cytek",
 baselinecutoffs=QC_Cutoffs, gainmultiplier = 2)
```

## {.sidebar}
Dashboard contains historical data from **2020** for the **Cytek Aurora 4L**.

**First Column: MFI** Median Fluorescent Intensity (MFI) values for QC beads acquired Before and After QC. Measures stability over time. 

**Second Column: Gain** Gain (Voltage) values set for instrument after QC. Changes over time reflective of laser health. 

**Third Colum: RCV** Percentage change of Robust Coefficient Variation (RCV) after QC. Higher values reflect decreased resolution between positive and negative for that detector.

For additional information concerning individual parameter tabs, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [UMGCC FCSS](https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/)

For additional flow cytometry resources, visit our [website](https://sites.google.com/view/umgcccflow/home)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)

```{r}
x <- The2020

# MFI
x <- x %>% dplyr::filter(Timepoint %in% c("Before", "After"))
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]

UltraVioletGains <- TheColumnNames[str_detect(TheColumnNames, "^UV")]
VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
#YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^YG")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheIntermediate[str_detect(TheIntermediate, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserDelayGains <- LaserGains[str_detect(LaserGains, "Delay")]
LaserDelayGains <- Luciernaga:::ColorPriority(LaserDelayGains)
LaserPowerGains <- LaserGains[str_detect(LaserGains, "Power")]
LaserPowerGains <- Luciernaga:::ColorPriority(LaserPowerGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)

UltraVioletPlotsMFI <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=UltraVioletGains,
                      plotType = "comparison", returntype = "plots",
                      Metadata="Timepoint", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=Maintenance)

VioletPlotsMFI <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=VioletGains,
                      plotType = "comparison", returntype = "plots",
                      Metadata="Timepoint", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=Maintenance)

BluePlotsMFI <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=BlueGains,
                      plotType = "comparison", returntype = "plots",
                      Metadata="Timepoint", strict = TRUE, YAxisLabel = "MFI",
                      RepairVisits=Maintenance)

RedPlotsMFI <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=RedGains,
                     plotType = "comparison", returntype = "plots",
                     Metadata="Timepoint", strict = TRUE, YAxisLabel = "MFI",
                     RepairVisits=Maintenance)

ScatterPlotsMFI <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=ScatterGains,
                     plotType = "comparison", returntype = "plots",
                     Metadata="Timepoint", strict = TRUE, YAxisLabel = " ",
                     RepairVisits=Maintenance)

LaserPlotsMFI <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=LaserGains,
                     plotType = "comparison", returntype = "plots",
                     Metadata="Timepoint", strict = TRUE, YAxisLabel = " ",
                     RepairVisits=Maintenance)
```

```{r}
#rCV
x <- x %>% dplyr::filter(Timepoint %in% c("After"))
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")
TheIntermediate <- TheColumns[!str_detect(TheColumns, "Gain")]
TheIntermediate <- TheIntermediate[str_detect(TheIntermediate, "rCV")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]

UltraVioletGains <- TheColumnNames[str_detect(TheColumnNames, "^UV")]
VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
#YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^YG")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserGains <- Luciernaga:::ColorPriority(LaserGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)
OtherGains <- c(ScatterGains)

UltraVioletPlotsRCV <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=UltraVioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV", RepairVisits=Maintenance)

VioletPlotsRCV <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV", RepairVisits=Maintenance)

BluePlotsRCV <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                      RepairVisits=Maintenance)

RedPlotsRCV <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "%rCV",
                     RepairVisits=Maintenance)

ScatterPlotsRCV <- QC_Plots(x=x, FailedFlag=TRUE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)
```

```{r}
# Gains

x <- x %>% dplyr::filter(Timepoint %in% c("After"))
TheColumns <- x %>% select(where(~is.numeric(.)||is.integer(.))) %>% colnames()
TheColumns <- setdiff(TheColumns, "TIME")
TheIntermediate <- TheColumns[str_detect(TheColumns, "Gain")]
TheColumnNames <- TheIntermediate[str_detect(TheIntermediate, "-A")]

UltraVioletGains <- TheColumnNames[str_detect(TheColumnNames, "^UV")]
VioletGains <- TheColumnNames[str_detect(TheColumnNames, "^V")]
BlueGains <- TheColumnNames[str_detect(TheColumnNames, "^B")]
#YellowGreenGains <- TheColumnNames[str_detect(TheColumnNames, "^YG")]
RedGains <- TheColumnNames[str_detect(TheColumnNames, "^R")]

ScatterGains <- TheColumnNames[str_detect(TheColumnNames, "SC-")]
ScatterGains <- Luciernaga:::ScalePriority(ScatterGains)
LaserGains <- TheColumns[str_detect(TheColumns, "Laser")]
LaserDelayGains <- LaserGains[str_detect(LaserGains, "Delay")]
LaserDelayGains <- Luciernaga:::ColorPriority(LaserDelayGains)
LaserPowerGains <- LaserGains[str_detect(LaserGains, "Power")]
LaserPowerGains <- Luciernaga:::ColorPriority(LaserPowerGains)
ScalingGains <- TheColumns[str_detect(TheColumns, "Scaling")]
ScalingGains <- Luciernaga:::ColorPriority(ScalingGains)

UltraVioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=UltraVioletGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=Maintenance)

VioletPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=VioletGains,
                      plotType = "individual", returntype = "plots", strict = TRUE, YAxisLabel = "Gain",
                      RepairVisits=Maintenance)

BluePlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=BlueGains,
                      plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                      RepairVisits=Maintenance)

RedPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=RedGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = "Gain",
                     RepairVisits=Maintenance)

ScatterPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScatterGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)

LaserDelayPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=LaserDelayGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)

ScalingPlotsGain <- QC_Plots(x=x, FailedFlag=FALSE, MeasurementType=ScalingGains,
                     plotType = "individual", returntype = "plots", YAxisLabel = " ",
                     RepairVisits=Maintenance)                     
```

```{r}
#| include: false
#| echo: false
PDFPlots <- c(UltraVioletPlotsMFI, VioletPlotsMFI, BluePlotsMFI, RedPlotsMFI, LaserPlotsMFI, ScatterPlotsMFI, UltraVioletPlotsGain, VioletPlotsGain, BluePlotsGain, RedPlotsGain, ScatterPlotsGain, LaserDelayPlotsGain, ScalingPlotsGain, UltraVioletPlotsRCV, VioletPlotsRCV, BluePlotsRCV, RedPlotsRCV, ScatterPlotsRCV)

Filename <- paste0("Historical_Aurora4L_2020")

MainFolder <- getwd()
MainFolder <- file.path(MainFolder, "data")

PDF <- Utility_Patchwork(x=PDFPlots, filename=Filename, returntype="pdf", outfolder=MainFolder, thecolumns=1)

CSVname <- paste0("Historical_Aurora4L_2020.csv")
SaveHere <- file.path(MainFolder, CSVname)
write.csv(The2020, SaveHere, row.names=FALSE)
```


## MFI {.tabset}

```{r}
#| title: UltraViolet
ggplotly(UltraVioletPlotsMFI[[1]])
ggplotly(UltraVioletPlotsMFI[[2]])
ggplotly(UltraVioletPlotsMFI[[3]])
ggplotly(UltraVioletPlotsMFI[[4]])
ggplotly(UltraVioletPlotsMFI[[5]])
ggplotly(UltraVioletPlotsMFI[[6]])
ggplotly(UltraVioletPlotsMFI[[7]])
ggplotly(UltraVioletPlotsMFI[[8]])
ggplotly(UltraVioletPlotsMFI[[9]])
ggplotly(UltraVioletPlotsMFI[[10]])
ggplotly(UltraVioletPlotsMFI[[11]])
ggplotly(UltraVioletPlotsMFI[[12]])
ggplotly(UltraVioletPlotsMFI[[13]])
ggplotly(UltraVioletPlotsMFI[[14]])
ggplotly(UltraVioletPlotsMFI[[15]])
ggplotly(UltraVioletPlotsMFI[[16]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsMFI[[1]])
ggplotly(VioletPlotsMFI[[2]])
ggplotly(VioletPlotsMFI[[3]])
ggplotly(VioletPlotsMFI[[4]])
ggplotly(VioletPlotsMFI[[5]])
ggplotly(VioletPlotsMFI[[6]])
ggplotly(VioletPlotsMFI[[7]])
ggplotly(VioletPlotsMFI[[8]])
ggplotly(VioletPlotsMFI[[9]])
ggplotly(VioletPlotsMFI[[10]])
ggplotly(VioletPlotsMFI[[11]])
ggplotly(VioletPlotsMFI[[12]])
ggplotly(VioletPlotsMFI[[13]])
ggplotly(VioletPlotsMFI[[14]])
ggplotly(VioletPlotsMFI[[15]])
ggplotly(VioletPlotsMFI[[16]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsMFI[[1]])
ggplotly(BluePlotsMFI[[2]])
ggplotly(BluePlotsMFI[[3]])
ggplotly(BluePlotsMFI[[4]])
ggplotly(BluePlotsMFI[[5]])
ggplotly(BluePlotsMFI[[6]])
ggplotly(BluePlotsMFI[[7]])
ggplotly(BluePlotsMFI[[8]])
ggplotly(BluePlotsMFI[[9]])
ggplotly(BluePlotsMFI[[10]])
ggplotly(BluePlotsMFI[[11]])
ggplotly(BluePlotsMFI[[12]])
ggplotly(BluePlotsMFI[[13]])
ggplotly(BluePlotsMFI[[14]])
```

```{r}
#| title: Red
ggplotly(RedPlotsMFI[[1]])
ggplotly(RedPlotsMFI[[2]])
ggplotly(RedPlotsMFI[[3]])
ggplotly(RedPlotsMFI[[4]])
ggplotly(RedPlotsMFI[[5]])
ggplotly(RedPlotsMFI[[6]])
ggplotly(RedPlotsMFI[[7]])
ggplotly(RedPlotsMFI[[8]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsMFI[[1]])
ggplotly(ScatterPlotsMFI[[2]])
ggplotly(ScatterPlotsMFI[[3]])
ggplotly(ScatterPlotsMFI[[4]])
ggplotly(ScatterPlotsMFI[[5]])
ggplotly(ScatterPlotsMFI[[6]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserDelayPlotsGain[[1]])
ggplotly(LaserDelayPlotsGain[[2]])
ggplotly(LaserDelayPlotsGain[[3]])
ggplotly(LaserDelayPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

## Gain {.tabset}

```{r}
#| title: UltraViolet
ggplotly(UltraVioletPlotsGain[[1]])
ggplotly(UltraVioletPlotsGain[[2]])
ggplotly(UltraVioletPlotsGain[[3]])
ggplotly(UltraVioletPlotsGain[[4]])
ggplotly(UltraVioletPlotsGain[[5]])
ggplotly(UltraVioletPlotsGain[[6]])
ggplotly(UltraVioletPlotsGain[[7]])
ggplotly(UltraVioletPlotsGain[[8]])
ggplotly(UltraVioletPlotsGain[[9]])
ggplotly(UltraVioletPlotsGain[[10]])
ggplotly(UltraVioletPlotsGain[[11]])
ggplotly(UltraVioletPlotsGain[[12]])
ggplotly(UltraVioletPlotsGain[[13]])
ggplotly(UltraVioletPlotsGain[[14]])
ggplotly(UltraVioletPlotsGain[[15]])
ggplotly(UltraVioletPlotsGain[[16]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsGain[[1]])
ggplotly(VioletPlotsGain[[2]])
ggplotly(VioletPlotsGain[[3]])
ggplotly(VioletPlotsGain[[4]])
ggplotly(VioletPlotsGain[[5]])
ggplotly(VioletPlotsGain[[6]])
ggplotly(VioletPlotsGain[[7]])
ggplotly(VioletPlotsGain[[8]])
ggplotly(VioletPlotsGain[[9]])
ggplotly(VioletPlotsGain[[10]])
ggplotly(VioletPlotsGain[[11]])
ggplotly(VioletPlotsGain[[12]])
ggplotly(VioletPlotsGain[[13]])
ggplotly(VioletPlotsGain[[14]])
ggplotly(VioletPlotsGain[[15]])
ggplotly(VioletPlotsGain[[16]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsGain[[1]])
ggplotly(BluePlotsGain[[2]])
ggplotly(BluePlotsGain[[3]])
ggplotly(BluePlotsGain[[4]])
ggplotly(BluePlotsGain[[5]])
ggplotly(BluePlotsGain[[6]])
ggplotly(BluePlotsGain[[7]])
ggplotly(BluePlotsGain[[8]])
ggplotly(BluePlotsGain[[9]])
ggplotly(BluePlotsGain[[10]])
ggplotly(BluePlotsGain[[11]])
ggplotly(BluePlotsGain[[12]])
ggplotly(BluePlotsGain[[13]])
ggplotly(BluePlotsGain[[14]])
```

```{r}
#| title: Red
ggplotly(RedPlotsGain[[1]])
ggplotly(RedPlotsGain[[2]])
ggplotly(RedPlotsGain[[3]])
ggplotly(RedPlotsGain[[4]])
ggplotly(RedPlotsGain[[5]])
ggplotly(RedPlotsGain[[6]])
ggplotly(RedPlotsGain[[7]])
ggplotly(RedPlotsGain[[8]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsGain[[1]])
ggplotly(LaserPlotsMFI[[2]])
ggplotly(ScatterPlotsGain[[2]])
ggplotly(ScatterPlotsGain[[3]])
ggplotly(LaserPlotsMFI[[2]])
ggplotly(LaserPlotsMFI[[2]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserDelayPlotsGain[[1]])
ggplotly(LaserDelayPlotsGain[[2]])
ggplotly(LaserDelayPlotsGain[[3]])
ggplotly(LaserDelayPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

## RCV {.tabset}

```{r}
#| title: UltraViolet
ggplotly(UltraVioletPlotsRCV[[1]])
ggplotly(UltraVioletPlotsRCV[[2]])
ggplotly(UltraVioletPlotsRCV[[3]])
ggplotly(UltraVioletPlotsRCV[[4]])
ggplotly(UltraVioletPlotsRCV[[5]])
ggplotly(UltraVioletPlotsRCV[[6]])
ggplotly(UltraVioletPlotsRCV[[7]])
ggplotly(UltraVioletPlotsRCV[[8]])
ggplotly(UltraVioletPlotsRCV[[9]])
ggplotly(UltraVioletPlotsRCV[[10]])
ggplotly(UltraVioletPlotsRCV[[11]])
ggplotly(UltraVioletPlotsRCV[[12]])
ggplotly(UltraVioletPlotsRCV[[13]])
ggplotly(UltraVioletPlotsRCV[[14]])
ggplotly(UltraVioletPlotsRCV[[15]])
ggplotly(UltraVioletPlotsRCV[[16]])
```

```{r}
#| title: Violet
ggplotly(VioletPlotsRCV[[1]])
ggplotly(VioletPlotsRCV[[2]])
ggplotly(VioletPlotsRCV[[3]])
ggplotly(VioletPlotsRCV[[4]])
ggplotly(VioletPlotsRCV[[5]])
ggplotly(VioletPlotsRCV[[6]])
ggplotly(VioletPlotsRCV[[7]])
ggplotly(VioletPlotsRCV[[8]])
ggplotly(VioletPlotsRCV[[9]])
ggplotly(VioletPlotsRCV[[10]])
ggplotly(VioletPlotsRCV[[11]])
ggplotly(VioletPlotsRCV[[12]])
ggplotly(VioletPlotsRCV[[13]])
ggplotly(VioletPlotsRCV[[14]])
ggplotly(VioletPlotsRCV[[15]])
ggplotly(VioletPlotsRCV[[16]])
```

```{r}
#| title: Blue
ggplotly(BluePlotsRCV[[1]])
ggplotly(BluePlotsRCV[[2]])
ggplotly(BluePlotsRCV[[3]])
ggplotly(BluePlotsRCV[[4]])
ggplotly(BluePlotsRCV[[5]])
ggplotly(BluePlotsRCV[[6]])
ggplotly(BluePlotsRCV[[7]])
ggplotly(BluePlotsRCV[[8]])
ggplotly(BluePlotsRCV[[9]])
ggplotly(BluePlotsRCV[[10]])
ggplotly(BluePlotsRCV[[11]])
ggplotly(BluePlotsRCV[[12]])
ggplotly(BluePlotsRCV[[13]])
ggplotly(BluePlotsRCV[[14]])
```

```{r}
#| title: Red
ggplotly(RedPlotsRCV[[1]])
ggplotly(RedPlotsRCV[[2]])
ggplotly(RedPlotsRCV[[3]])
ggplotly(RedPlotsRCV[[4]])
ggplotly(RedPlotsRCV[[5]])
ggplotly(RedPlotsRCV[[6]])
ggplotly(RedPlotsRCV[[7]])
ggplotly(RedPlotsRCV[[8]])
```

```{r}
#| title: Scatter
ggplotly(ScatterPlotsRCV[[1]])
ggplotly(LaserPlotsMFI[[2]])
ggplotly(ScatterPlotsRCV[[2]])
ggplotly(ScatterPlotsRCV[[3]])
ggplotly(LaserPlotsMFI[[2]])
ggplotly(LaserPlotsMFI[[2]])
```

```{r}
#| title: LaserDelay
ggplotly(LaserDelayPlotsGain[[1]])
ggplotly(LaserDelayPlotsGain[[2]])
ggplotly(LaserDelayPlotsGain[[3]])
ggplotly(LaserDelayPlotsGain[[4]])
```

```{r}
#| title: LaserScaling
ggplotly(ScalingPlotsGain[[1]])
ggplotly(ScalingPlotsGain[[2]])
ggplotly(ScalingPlotsGain[[3]])
ggplotly(ScalingPlotsGain[[4]])
```

